Enhanced Residual Context-based Networks for Image Outpainting

### 2020-05-12 tex/paper.tex
Report update

% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

@@

\icmlcorrespondingauthor{Przemek Gardias}{pmgardias@wpi.edu}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{boring formatting information, machine learning, ICML}

@@

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c|c}  
    \hline
    \textbf{layer} & \textbf{output size} & \textbf{parameters}\\ 
    \hline
      Conv & 16$\times$192$\times$192 & 5$\times$5, stride=1 \\
    \hline
      ResBlock & 128$\times$96$\times$96 & 3$\times$3, stride=2 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=2 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Trans-Conv & 128$\times$96$\times$96 & 4$\times$4, stride=1 \\
    \hline
      ReLU & 128$\times$96$\times$96 & None \\
    \hline
      Conv & 128$\times$96$\times$96 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 128$\times$96$\times$96 & None \\
    \hline
      Trans-Conv & 64$\times$192$\times$192 & None \\
    \hline
      ReLU & 64$\times$192$\times$192 & None \\
    \hline
      Conv & 32$\times$192$\times$192 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 32$\times$192$\times$192 & None \\
    \hline
      Conv & 3$\times$192$\times$192 & 3$\times$3, stride=2 \\
    \hline
      Sigmoid & 3$\times$192$\times$192 & None \\
    \hline
    \end{tabular}

@@

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c}  
    \hline
    \textbf{layer} & \textbf{parameters}\\ 
    \hline
      Conv & 3$\times$3, stride=\(s_{in}\) \\
    \hline
      ReLU & None \\
    \hline
      Conv & 3$\times$3, stride=\(s_{in}\) \\
    \hline
      ReLU & None \\
    \hline
      Add & None \\
    \hline
    \end{tabular}

@@

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c}  
    \hline
    \textbf{layer} & \textbf{parameters}\\ 
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=1 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=1 \\
    \hline

@@

  \caption{Architecture of global and local discriminators.} 
  \label{tab:3}
  \label{table3} 
\end{table}

@@

@@

\bibliography{example_paper}
\bibliographystyle{cs541}

>>>>

% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure} 
\usepackage{amsmath}

@@

\icmlcorrespondingauthor{}{\{pmgardias, etarthur, hsun2\}@wpi.edu}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{image outpainting, generative adversarial network, context encoder, computer vision, deep learning, machine learning, ICML}

@@

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c|c}  
    \hline
    \textbf{layer} & \textbf{output size} & \textbf{parameters}\\ 
    \hline \hline
      Conv & 16$\times$192$\times$192 & 5$\times$5, stride=1 \\
    \hline
      ResBlock & 128$\times$96$\times$96 & 3$\times$3, stride=2 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=2 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ResBlock & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Conv & 256$\times$48$\times$48 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 256$\times$48$\times$48 & None \\
    \hline
      Trans-Conv & 128$\times$96$\times$96 & 4$\times$4, stride=1 \\
    \hline
      ReLU & 128$\times$96$\times$96 & None \\
    \hline
      Conv & 128$\times$96$\times$96 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 128$\times$96$\times$96 & None \\
    \hline
      Trans-Conv & 64$\times$192$\times$192 & None \\
    \hline
      ReLU & 64$\times$192$\times$192 & None \\
    \hline
      Conv & 32$\times$192$\times$192 & 3$\times$3, stride=1 \\
    \hline
      ReLU & 32$\times$192$\times$192 & None \\
    \hline
      Conv & 3$\times$192$\times$192 & 3$\times$3, stride=2 \\
    \hline
      Sigmoid & 3$\times$192$\times$192 & None \\
    \hline
    \end{tabular}

@@

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c}  
    \hline
    \textbf{Layer} & \textbf{Parameters}\\ 
    \hline \hline
      Conv & 3$\times$3, stride=\(s_{in}\) \\
    \hline
      ReLU & None \\
    \hline
      Conv & 3$\times$3, stride=\(s_{in}\) \\
    \hline
      ReLU & None \\
    \hline
      Add & None \\
    \hline
    \end{tabular}

@@

\begin{table}[h] 
  \centering  
    \begin{tabular}{c|c}  
    \hline
    \textbf{Layer} & \textbf{Parameters}\\ 
    \hline \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=2 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=1 \\
    \hline
      InstanceNorm & None \\
    \hline
      LeakyReLU & negative slope=0.2, inplace=True \\
    \hline
      Conv & 3$\times$3, stride=1 \\
    \hline

@@

  \caption{Architecture of global and local discriminators $D_G$ and $D_L$, respectively.} 
  \label{tab:3}
  \label{table3} 
\end{table}

@@

Training is done for 50 epochs, with a fixed learning rate of $\alpha=0.0003$ and two Adam optimizers with $\beta_1=0.5, \beta_2=0.999$, following the same hyperparameters proposed in Van Hoorick 2020 \cite{van_hoorick_image_2020} The loss functions are as follows:
\begin{align}
  L_{rec} &= ||x-G(x)||_1 \\
  L_{adv} &= ||D(G(x))-1||_2^2 \\
  L_G &= \lambda_{rec}L_{rec} + \lambda_{adv}L_{adv} \\
  L_D &= ||D(x)-1||_2^2 + ||D(G(x))-0||_2^2
\end{align}

We apply a time based remedy to the generator loss function that punishes the generator heavier for bad outputs as time progresses.

\begin{align}
  \lambda_{adv}(n) = \begin{cases}
    0.001, & \text{if }n\leq10 \\
    0.005, & \text{if }10<n\leq30 \\
    0.015, & \text{otherwise}
  \end{cases}
  \label{eq:loss_adv}
\end{align}

Since humans still perform vastly greater than deep learning networks at this task we conclude our experiment with a qualitative discussion about the quality of hallucinations. As many previously mentioned models in this domain create noise or lines that are clearly out of place in the hallucinations, we aim to manually evaluate whether our model rectifies this issue or these manifestations are still present.

@@

\bibliography{paper.bib}
\bibliographystyle{cs541}
